\documentclass{article}[12pt]

\usepackage[top=1in,bottom=1in,right=1in,left=1in]{geometry}

\begin{document}


\title{Homework Assignment 1B - Reading}
\date{September 5, 2019}

\author{
   FirstName LastName \\
   netid@email.arizona.edu
}

\maketitle

\noindent
{\bf 1. What problem is this paper trying to solve?}

\vspace{2ex}\noindent
{\bf 2. Why is this problem considered a visualization problem?}

\vspace{2ex}\noindent
{\bf 3. Why is the problem important?}

\vspace{2ex}\noindent
{\bf 4. How does this paper contribute to solving the problem?} 

\vspace{2ex}\noindent
{\bf 5. What approaches are used to construct the contributions?}

\vspace{2ex}\noindent
{\bf 6. How are the contributions of the paper evaluated or justified?} 

\vspace{2ex}\noindent
{\bf 7. What do you think are this paper's strengths?} 

\vspace{2ex}\noindent
{\bf 8. What do you think could be improved about this paper?}

\vspace{2ex}\noindent
{\bf 9. What future directions do the authors suggest?}

\vspace{2ex}\noindent
{\bf 10. What future directions not mentioned in the paper would you suggest?}

\vspace{2ex}\noindent
{\bf 11. What questions do you have about this paper? For example: Were these things
   you find difficult to understand? Are there details left unanswered? Do you
have philosophical questions regarding some of the points made?}

\vspace{2ex}\noindent
{\bf 12. How might the concepts or approaches in this paper relate to your course
   project? If you have not yet chosen a course project, give your best guess
with what you are thinking of doing now.}





\end{document}
